---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# valorantshiny

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of valorantshiny is to make it easy to play minigames like strat/agent roulette.

Find the app online at: https://selkamand.shinyapps.io/valorantshiny/

## Installation

You can install the development version of valorantshiny like so:

``` r
remotes::install_github('selkamand/valorantshiny')
```

## Quick start

Start the shiny app by running the following
```{r example, eval = FALSE}
library(valorantshiny)

run_app()
```

## Code of Conduct

Please note that the valorantshiny project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
